Precise predictions for same-sign W-bosons scattering at the LHC

### 2018-02-02 Draft/scanNLO.tex
scanNLO.tex: modified wrong figure names

{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_tu.pdf}}

@@

{\includegraphics[scale=0.39]{figures/scanfigures/a6as_VBFNLOVSrecola_stu.pdf}}

>>>>

{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_tu.pdf}}

@@

{\includegraphics[scale=0.39]{figures/scanfigures/a6as_vbfnloVSrecola_stu.pdf}}
